\subsection{Account Synchronization}
\
If new users are allowed to register at a generalized UppreSSO system after the initialization,
in order to distinguish meaningful accounts from meaningless ones,
 an RP needs to regularly synchronize its accounts from the IdP,
 especially when it does not check $PID_{RP}$ before accepting an identity token.
For example,
    when an account is derived but not in the visited RP's local account list,
        the RP will contact the IdP to synchronize accounts.
Then, after the instant account synchronization, 
    the token holder will be rejected
     if the derived account is still considered as meaningless (i.e., not in the RP's local account list).

In this case, an RP cannot imperceptively treat the token holder with a derived account not in the list
 as a newly-registered user.
Although a malicious user cannot log into this RP as any meaningful account belonging to other users according to Theorems \ref{theorem-uid-wo-checking} and \ref{theorem-rp-wo-checking},
 she could log into such an RP as an \emph{identical} meaningless account in several logins.
For example, both $\hat{t}$ and $\check{t}$ ($\check{t} \neq \hat{t}$) are reused in these logins,
    as analyzed in the proof of Theorem \ref{theorem-uid-wo-checking}.
Then, this user actually owns multiple accounts at one RP.
%\footnote{In this case, $\hat{t}$ and $\check{t}$ are long-term secrets kept by the malicious user, and $\check{t}$ is sent to the RP. For such a malicious user, the system actually provides services of identity federation. Then, even when the IdP is colluding with RPs, the ``meaningless'' accounts belong to this user across RPs cannot be linked because $\hat{t}$ masks the relationship among these accounts.}


This instant account synchronization can be alternatively finished by conditional $PID_{RP}$ checking as below.
If an RP derives some account not in its local account list from a signed token without checking $PID_{RP}$,
    it then checks $PID_{RP}$ in this case:
     If $PID_{RP}$ enclosed in the token is equal to $\mathcal{BL}(x,t,\omega)$,
                this account is asserted to belong to a newly-registered user
                and the RP updates its account list locally;
    otherwise, it rejects this token.


